%
% 6.857 homework template
%
% NOTE:
% Be sure to define your team members with the \team command
% Be sure to define the problem set with the \ps command
% Be sure to use the \answer command for each of your answers 
\documentclass[11pt]{article}

\newcommand{\team}{ Erica Du \\ Skanda Koppula \\ Jessica Wang }
\newcommand{\ps}{ Problem Set 1 }

%\pagestyle{headings}
\usepackage{amsfonts}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\setlength{\parskip}{1pc}
\setlength{\parindent}{0pt}
\setlength{\topmargin}{-3pc}
\setlength{\textheight}{9.5in}
\setlength{\oddsidemargin}{0pc}
\setlength{\evensidemargin}{0pc}
\setlength{\textwidth}{6.5in}

\newcommand{\answer}[1]{
\newpage
\noindent
\framebox{
	\vbox{
		6.857 Homework \hfill {\bf \ps} \hfill \# #1  \\ 
		\team \hfill \today
	}
}
\bigskip

}


\begin{document}

\answer{1-3 - Subverting Cryptography}
\begin{enumerate}
\item Insecure implementation: the implementation of a theoretically secure algorithms might have vulnerabilities
	\begin{itemize}
	\item The OpenSSL library this year was revealed to have a buffer over-read bug, Heartbleed.
	\item The NSA has inserted faulty code/backdoors in commonly used random number generators.
	\end{itemize}
	\textbf{DEFENSE: } Verify 3rd party code. Otherwise implement and test everything, like random number generators, on your own.
\item Improper use: users may misuse otherwise secure software and/or algorithms
	\begin{itemize}
	\item Users may create short or weak keys
	\item Users may re-use passwords
	\end{itemize}
	\textbf{DEFENSE: } Create strong restrictions for user inputs to ensure strong key creation.
\item Hardware injection: tampering with physical devices
	\begin{itemize}
	\item Hardware keyloggers to track keystrokes and potentially passwords
	\item Inserting backdoors into internet routers
	\end{itemize}
	\textbf{DEFENSE: } Only use devices from a trusted resource, only use devices you create yourself (i.e. create all your own routers and keyboards).
\item Government: Legal Retrieval 
	\begin{itemize}
	\item Court orders to obtain private keys (compulsion)
	\item Abusing trust commercial trust has in a body like the NSA, and just asking for the data
	\end{itemize}
	\textbf{DEFENSE: } Host data in a different country, start your own country without these rules. Don't put your trust in governmental bodies, or other bodies of "authority." Get a good lawyer. 
\item Social engineering: extracting personal information to gain useful information
	\begin{itemize}
	\item Email or phone phishing
	\end{itemize}
	\textbf{DEFENSE: } Adblock. Spam filters. Common Sense.
\item Indirect Computational Data
	\begin{itemize}
	\item Timing attacks (i.e. side channel timing attacks) that determine message based on how long it 
	\item Using metadata of a message to learn information about the messagetakes per step of computation
	\end{itemize}
	\textbf{DEFENSE: } Introduce more randomness (i.e. in length) into actual message, to make timing more uniform. Introduce randomness into metadata.
\item Coercion: bribery and corruption
	\begin{itemize}
	\item Pay NSA employees more than the government to spill secrets
	\item Give money in exchange for information
	\end{itemize}
	\textbf{DEFENSE: } Pay your employees a sufficient wage. Only hire people you trust.
\item Go after key aggregators instead of the actual message.
	\begin{itemize}
	\item Instead of trying to break the crypto, just try to steal the keys.
	\end{itemize}
	\textbf{DEFENSE: } Don't use key aggregators. Use one-time keys.

\end{enumerate}

\end{document}

